### 2020-11-11 cv/cv-body.tex
Update CV

\begin{description}
\tightlist
\item[2017--20]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2020--20]
Adjunct Professor, Department of Mathematics, Simon Fraser University\\
\item[2019--20]
Associate Editor, the Canadian Journal of Fisheries and Aquatic Sciences
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

time-series data. In press at The R Journal.
\href{https://journal.r-project.org/archive/2019/RJ-2019-007/RJ-2019-007.pdf}{https://doi.org/10.32614/RJ-2019-007}.

@@

\begin{description}
\tightlist
\item[2019]
\textbf{Anderson, S.C.}, Keppel, E.A., Edwards, A.M. 2019. A
reproducible data synopsis for over 100 species of British Columbia
groundfish. DFO Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version})
\item[2018]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018. In press.
\end{description}

@@

\begin{description}
\tightlist
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2019]
\textbf{rosettafish}: An R package for translating fish- and
fisheries-related terms.\\
\url{https://github.com/pbs-assess/rosettafish}
\item[2019]
\textbf{sdmTMB}: An R package for fitting spatiotemporal species
distribution 9GLMMs (generalized linear mixed effects models) with TMB
(Template Model Builder)\\
\url{https://github.com/pbs-assess/sdmTMB}
\item[2019]
\textbf{gfplot} \& \textbf{gfsynopsis}: R packages to generate an annual
Research Document synopsis report showing all available fishery and
biological data and basic model fits for 109 Pacific groundfish species
for publication through the Canadian Science Advisory Secretariat
(CSAS). To be reviewed via regional peer-review meeting November 22--23
2018.\\
\url{https://github.com/pbs-assess/gfplot} and
\url{https://github.com/pbs-assess/gfsynopsis}
\item[2019]
\textbf{csasdown}: Reproducible Canadian Science Advisory Secretariat
Research Documents via R Markdown.\\
\url{https://github.com/pbs-assess/csasdown}
\item[2018]
\textbf{glmmfields}: Generalized linear mixed models with robust random
fields for spatiotemporal modeling.\\
\url{https://cran.r-project.org/package=glmmfields}
\item[2017]
\textbf{datalimited}: Stock assessment methods for data-limited
fisheries. \url{https://github.com/datalimited/datalimited}
\item[2014]
\textbf{Anderson, S.C.}, J.W. Moore, M.M McClure, N.K. Dulvy, A.B.
Cooper.\\
\textbf{metafolio}: Metapopulation simulations for conserving salmon
through portfolio optimization.
\url{http://cran.r-project.org/package=metafolio}
\item[2013]
\textbf{Anderson, S.C.}, C.C. Monnahan, K.F. Johnson, K. Ono, J.L.
Valero, C.J Cunningham, F. Hurtado-Ferro, R. Licandeo, C.R. McGilliard,
C.S. Szuwalski, K.A. Vert-pre, A.R. Whitten. \textbf{ss3sim}: Fisheries
stock assessment simulation testing with Stock Synthesis.
\url{http://cran.r-project.org/package=ss3sim}
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. \textbf{ecofolio}:
Tools to quantify metapopulation portfolio effects.
\url{https://github.com/seananderson/ecofolio}
\end{description}

\hypertarget{invited-talks-and-conference-presentations}{%
\section{Invited talks and conference
presentations}\label{invited-talks-and-conference-presentations}}

\begin{description}
\tightlist
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, P.A. English, E.J.
Ward. An automated synopsis of the state of Pacific Canadian groundfish
and climate impacts. North Pacific Marine Science Organization (PICES)
conference. Victoria, BC, Canada. Invited talk to plenary session (to be
given October 2019).
\item[2018]
\textbf{Anderson, S.C.}, Ward, E. J. Black swans in space: modelling
spatiotemporal processes with extremes. International Statistical
Ecology Conference, St.\ Andrews, Scotland.
(\href{https://www.dropbox.com/s/ufce52ocpycftk1/anderson-ward-isec-2018.pdf?dl=1}{slides})
\item[2017]
\textbf{Anderson, S.C.} Data-driven approaches to quantifying population
status and extremes. Early Career Award keynote lecture at the Canadian
Society for Ecology and Evolution (CSEE), Victoria, BC, Canada.
\item[2016]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. North America Congress for
Conservation Biology, Madison, WI, United States.
\item[2016]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
World Fisheries Conference, Busan, South Korea. (Presented \emph{in
absentia} by J.T. Thorson.)
\item[2015]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
American Fisheries Society Annual Meeting, Portland, OR, United States.
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
challenges of quantifying ecological portfolios
(\href{http://seananderson.ca/talks/2013/PE_SAFS_quantsem.pdf}{slides}),
Quantitative Seminar, School of Aquatic and Fishery Sciences, University
of Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
ecological portfolio effect overestimates the benefit of diversity.
School of Aquatic and Fishery Sciences, University of Washington,
Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. Metapopulation
dynamics and the generality of the ecological portfolio effect. Les
Ecologistes Departmental Seminar, Simon Fraser University, Burnaby, BC,
Canada.
\item[2010]
\textbf{Anderson, S.C.} The rise of invertebrates, the fall of sea
cucumbers, and the risk of maturing late. Earth2Ocean Research Group,
Simon Fraser University, Burnaby, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E. Mills Flemming, R. Watson, H.K. Lotze.
Ecosystem impacts of the global expansion of invertebrate fisheries.
International Oceans Past II Conference \emph{Multidisciplinary
Perspectives on the History and Future of Marine Animal Populations}.
Vancouver, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E Mills Flemming, R. Watson, H.K. Lotze.
Global invertebrate fisheries: trends and consequences. NCEAS (National
Center for Ecological Analysis and Synthesis) Working Group
\emph{Finding Common Ground in Marine Conservation and Management}.
Santa Barbara, CA, USA.
\item[2009]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Harvest Fisheries Seminar Series. Bedford Institute of
Oceanography, Fisheries and Oceans, Dartmouth, NS, Canada.
\item[2008]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Departmental Seminar, Biology Department, Dalhousie University,
Canada.
\end{description}

@@

@@

@@

\hypertarget{contract-employment}{%
\section{Contract employment}\label{contract-employment}}

\begin{description}
\tightlist
\item[2014--15]
Data analysis in R and C++ for Ecoscape Environmental Consultants Ltd.
\item[2013]
Co-developed global fisheries status maps for the
\href{http://ramlegacy.org/}{RAM Legacy Stock Assessment Database} for
R. Hilborn
\item[2010]
Assessment of Arctic surfclam on Banquereau Bank using
industry-collected data for Clearwater Seafoods, Bedford, NS, Canada.
\item[2010]
Modelling length-frequency distribution changes of Atlantic halibut for
NAFO Divisions 4VWX5Z and 3NOP for Dr.\ K. Trzcinski, Population Ecology
Division, Bedford Institute of Oceanography, Fisheries and Oceans,
Dartmouth, NS, Canada.
\end{description}

@@

\begin{description}
\tightlist
\item[2019]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{Spatial ecosystem state and
pressure indicators and the scale-dependence of temporal indicator
performance in the California Current and beyond}
\item[2018--19]
European Commission Joint Research Council working group \emph{A new
approach to strengthen evidence-based fisheries management}
investigating approaches to providing fisheries management scientific
advice based on model ensembles.
\item[2016--17]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{An early-warning index for
abrupt change in northeast Pacific ecosystems}
\item[2015--16]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) \emph{Applying portfolio effects to the Gulf of Alaska
ecosystem: Did multi-scale diversity buffer against the Exxon Valdez oil
spill?} (\href{https://www.nceas.ucsb.edu/featured/marshall}{URL})
\item[2015--16]
Gordon and Betty Moore Foundation funded working group \emph{Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks}.
\item[2011--13]
NESCent (National Evolutionary Synthesis Center, Durham, NC) Working
Group \emph{Determinants of Extinction in Ancient and Modern Seas} led
by Paul Harnik, Seth Finnegan, and Rowan Lockwood.
(\href{http://www.nescent.org/science/awards_summary.php?id=256}{URL})
\item[2010]
Atlantic Halibut Assessment Science Peer Review Meeting, Fisheries and
Oceans, Dartmouth, NS, Canada.
\item[2007--09]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) Distributed Graduate Seminar, in association with the
Working Group \emph{Finding Common Ground in Marine Conservation and
Management} led by Ray Hilborn and Boris Worm.
(\href{http://www.nceas.ucsb.edu/projects/12307}{URL})
\item[2008]
Workshop on Canadian Science and Management Strategies for Sea Cucumber
(\emph{Cucumaria frondosa}), Fisheries and Oceans, Dartmouth, NS, Canada
(work presented \emph{in absentia}).
\item[2007]
Workshop on Canadian Science and Management Strategies for Atlantic
Hagfish, Fisheries and Oceans, Dartmouth, NS, Canada.
(\href{http://www.dfo-mpo.gc.ca/CSAS/Csas/Publications/Pro-CR/2009/2009_009_e.htm}{URL})
\end{description}

@@

Reviewer for Science, Ecology, Canadian Journal of Fisheries and Aquatic
Sciences, Fish and Fisheries, Ecological Applications, Conservation
Biology, Proceedings B, Marine Policy, Population Ecology, Journal of
Applied Ecology, International Journal of Tropical Biology and
Conservation, Biological Conservation, Oikos, Journal of Environmental
Management, Endangered Species Research, Aquatic Conservation

>>>>

\begin{description}
\tightlist
\item[2017--20]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\item[2019--20]
Associate Editor, the Canadian Journal of Fisheries and Aquatic Sciences
\item[2020--20]
Adjunct Professor, Department of Mathematics, Simon Fraser University
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

time-series data. The R Journal. 11(2):46--55.
\url{https://doi.org/10.32614/RJ-2019-007}.

@@

\begin{description}
\tightlist
\item[2020]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockﬁsh (\emph{Sebastes ruberrimus}) in British
Columbia. Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 11
2020.
(\href{https://www.dropbox.com/s/pll8axzsxqka8j8/resdoc-iye.pdf?dl=1}{English
version}).
\item[2020]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia.
Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 9 2020.
(\href{https://www.dropbox.com/s/rgxk2wco5v5zp0e/gfmp-2020-03-13.pdf?dl=1}{English
version}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

\hypertarget{dfo-technical-reports}{%
\section{DFO Technical Reports}\label{dfo-technical-reports}}

\begin{description}
\tightlist
\item[2019]
\textbf{Anderson, S.C.}, and Workman, G.D. A review of groundfish
surveys in 2018 and an introduction to the groundfish data synopsis
report. In State of the physical, biological and selected fishery
resources of Pacific Canadian marine ecosystems in 2018. Edited by J.L.
Boldt, J. Leonard, and P.C. Chandler. pp. 90--94. Can. Tech. Rep.\ Fish.
Aquat. Sci. 3314, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2018/index-eng.html}{English
version})
\item[2020]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 102--106. Can. Tech. Rep.\ Fish. Aquat. Sci. 3377, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2019/index-eng.html}{English
version})
\item[2018]
Edwards, A.M., Duplisea, D.E., Grinnell, M.H., \textbf{Anderson, S.C.},
Grandin, C.J., Ricard, D., Keppel, E.A., Anderson, E.D., Baker, K.D.,
Benoit, H.P., Cleary, J.S., Connors, B.M., Desgagnes, M., English, P.A.,
Fishman, D.F., Freshwater, C., Hedges, K.J., Holt, C.A., Holt, K.R.,
Kronlund, R., Mariscak, A., Obradovich, S.G., Patten, B.A., Rogers, B.,
Rooper, C.N., Simpson, M.R., Surette, T.J., Tallman, R.F., Wheeland,
L.J., Wor, C., and Zhu, X. 2018. Proceedings of the Technical Expertise
in Stock Assessment (TESA) national workshop on ``Tools for transparent,
traceable, and transferable assessments'' 27--30 November 2018 in
Nanaimo, British Columbia. Can. Tech. Rep.\ Fish. Aquat. Sci. 3290,
Nanaimo, BC.
(\href{https://waves-vagues.dfo-mpo.gc.ca/Library/40750152.pdf}{English
version})
\end{description}

@@

\begin{description}
\tightlist
\item[2020--21]
Co-principal Investigator on NOAA Office of Science and Technology
NMFS-DFO grant ``Characterizing range shifts in groundfish species in
response to local climate velocities''. An extension to apply methods
from a similarly titled ACCASP grant below to NOAA waters. (\$30K USD)
\item[2020--21]
Collaborator on NOAA Office of Science and Technology NMFS-DFO grant
``Groundfish distribution shifts between British Columbia, Canada, and
Southeast Alaska, USA: climate drivers, ecosystem impacts and management
implications''. (\$30K USD)
\item[2019]
Canadian Journal of Fisheries and Aquatic Sciences Stevenson
Lectureship. \url{http://www.nrcresearchpress.com/page/cjfas/award} A
``lectureship conferred upon a young, energetic and creative researcher
at the cutting edge of an aquatic discipline''.
\item[2018--20]
Principal Investigator of a two-year grant from Fisheries and Oceans
Canada's Aquatic Climate Change Adaptation Services Program (ACCASP).
Project title: Characterizing range shifts in British Columbia
groundfish species in response to local climate velocities.
\item[2017]
Canadian Society for Ecology and Evolution (CSEE) Early Career Award.\\
\url{http://csee-scee.ca/2017-early-career-awards/}
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship\\
\url{http://conbio.org/mini-sites/smith-fellows/meet-the-fellows/2015-fellows/sean-anderson}
\item[2015]
Simon Fraser University Dean of Graduate Studies Convocation Medal\\
\url{https://www.sfu.ca/dean-gradstudies/blog/year/2015/06/SeanAnderson.html}
\item[2014]
Garfield Weston Foundation / BC Packers Ltd.\ Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

@@

\setlist[itemize]{topsep=2pt}

\textbf{covidseir}: \url{https://github.com/seananderson/covidseir}

\begin{itemize}
\tightlist
\item
  Primary statistical model for COVID-19 forecasts for Canada (Public
  Health Agency of Canada) since August 2020 and British Columbia since
  April 2020
\item
  Fits a Bayesian SEIR (Susceptible, Exposed, Infectious, Recovered)
  model to daily COVID-19 case data
\item
  Can accommodate multiple types of case data at once (e.g., reported
  cases, hospitalizations, ICU admissions) and accounts for delays
  between symptom onset and case appearance.
\item
  Can evaluate epidemic forecasts given changes to population contact
  rates (e.g., levels of social distancing)
\item
  Published: Anderson et al.\ (2020; PLOS Computational Biology)
\end{itemize}

\textbf{sdmTMB}: \url{https://github.com/pbs-assess/sdmTMB}

\begin{itemize}
\tightlist
\item
  An R package for fitting spatiotemporal species distribution GLMMs
  (generalized linear mixed effects models) with TMB (Template Model
  Builder)
\end{itemize}

\textbf{glmmfields}: \url{https://cran.r-project.org/package=glmmfields}

\begin{itemize}
\tightlist
\item
  Bayesian generalized linear mixed models (GLMMs) with robust random
  fields for spatiotemporal modeling
\item
  Allows identification of extreme changes in spatial distribution
  (e.g., rapid range contractions)
\item
  Published: Anderson and Ward (2019; Ecology)
\end{itemize}

\textbf{bayesdfa}: \url{https://cran.r-project.org/package=bayesdfa}

\begin{itemize}
\tightlist
\item
  R package to fit Bayesian Dynamic Factor Analysis (DFA) time series
  models (co-developed with E.J. Ward)
\item
  Can identify common trends, extreme events, or regime shifts in
  multiple ecological timeseries
\item
  Published: Ward et al.\ (2019; The R Journal)
\end{itemize}

\textbf{csasdown}: \url{https://github.com/pbs-assess/csasdown}

\begin{itemize}
\tightlist
\item
  R package for reproducible Canadian Science Advisory Secretariat
  Research Documents, Science Responses, and Technical Reports via R
  Markdown
\item
  Enables fully reproducible CSAS reports going directly from databases
  to analysis to written reports to bring CSAS reports in line with
  modern data analysis best practices
\end{itemize}

\textbf{rosettafish}: \url{https://github.com/pbs-assess/rosettafish}

\begin{itemize}
\tightlist
\item
  Enables the seamless translation of fish- and fisheries-related terms
  in R code to enable reproducible and efficient production of bilingual
  CSAS Research Documents and Science Responses
\end{itemize}

\textbf{gfplot, gfdata, gfsynopsis, and gfdlm}:
\url{https://github.com/pbs-assess/}

\begin{itemize}
\tightlist
\item
  R packages to facilitate rapid and reproducible data extraction, model
  fitting, and plotting of BC groundfish data
\item
  gfsynopsis is used to generate an annual Research Document synopsis
  report showing all available fishery and biological data and model
  fits for 113 species
\item
  gfdlm facilitates applying the management strategy evaluation toolkit
  `MSEtool' to BC groundfish
\end{itemize}

\textbf{ss3sim}: \url{https://github.com/ss3sim/ss3sim}

\begin{itemize}
\tightlist
\item
  R package for flexible, rapid, and reproducible fisheries stock
  assessment simulation testing with the widely used Stock Synthesis
  statistical age-structured stock assessment framework
\item
  Published: Anderson et al.\ (2014; PLOS ONE)
\end{itemize}

\hypertarget{selected-first-author-invited-conference-presentations}{%
\section{Selected first-author invited conference
presentations}\label{selected-first-author-invited-conference-presentations}}

\begin{description}
\tightlist
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, P.A. English, E.J.
Ward. An automated synopsis of the state of Pacific Canadian groundfish
and climate impacts. North Pacific Marine Science Organization (PICES)
conference. Victoria, BC, Canada. Invited talk to plenary session (to be
given October 2019).
\item[2018]
\textbf{Anderson, S.C.}, Ward, E. J. Black swans in space: modelling
spatiotemporal processes with extremes. International Statistical
Ecology Conference, St.\ Andrews, Scotland.
(\href{https://www.dropbox.com/s/ufce52ocpycftk1/anderson-ward-isec-2018.pdf?dl=1}{slides})
\item[2017]
\textbf{Anderson, S.C.} Data-driven approaches to quantifying population
status and extremes. Early Career Award keynote lecture at the Canadian
Society for Ecology and Evolution (CSEE), Victoria, BC, Canada.
\item[2016]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. North America Congress for
Conservation Biology, Madison, WI, United States.
\item[2016]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
World Fisheries Conference, Busan, South Korea. (Presented \emph{in
absentia} by J.T. Thorson.)
\item[2015]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
American Fisheries Society Annual Meeting, Portland, OR, United States.
\end{description}

@@

Two webinars for the national TESA (Technical Expertise in Stock
Assessment) 2019--2020 webinar series: (1) data visualization with
ggplot2 and (2) efficiently iterating with code using the purrr package

@@

Organizer of \href{https://adv-r.hadley.nz/}{Advanced R} book club at
Pacific Biological Station. Organized seven twice-a-month meetings of
DFO Biologists and Research Scientists to work through the book and
clarify exercise material.

@@

@@

\begin{description}
\tightlist
\item[2020--23]
Joint ICES/PICES Working Group on impacts of warming on growth rates and
fisheries yields (WGGRAFY).
\item[2020--22]
TNC (The Nature Conservancy, based in the California office) working
group on climate change impacts on North American west coast fisheries
\item[2020]
Ocean Frontier Institute/Canadian Statistical Sciences Institute
(CANSSI) working group on \emph{Spatial Modelling of Fishery Survey Data
to Improve Stock Assessment}; invited keynote speaker
\item[2019--20]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{Spatial ecosystem state and
pressure indicators and the scale-dependence of temporal indicator
performance in the California Current and beyond}
\item[2018--19]
European Commission Joint Research Council working group \emph{A new
approach to strengthen evidence-based fisheries management}
investigating approaches to providing fisheries management scientific
advice based on model ensembles.
\item[2018]
Galway-Mayo Institute of Technology (Ireland) working group on ecosystem
tipping points
\item[2016--17]
NOAA (National Oceanic and Atmospheric Administration) FATE (Fisheries
and the Environment) working group \emph{An early-warning index for
abrupt change in northeast Pacific ecosystems}
\item[2015--16]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) \emph{Applying portfolio effects to the Gulf of Alaska
ecosystem: Did multi-scale diversity buffer against the Exxon Valdez oil
spill?} (\href{https://www.nceas.ucsb.edu/featured/marshall}{URL})
\item[2015--16]
Gordon and Betty Moore Foundation funded working group \emph{Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks}.
\item[2011--13]
NESCent (National Evolutionary Synthesis Center, Durham, NC) Working
Group \emph{Determinants of Extinction in Ancient and Modern Seas} led
by Paul Harnik, Seth Finnegan, and Rowan Lockwood.
(\href{http://www.nescent.org/science/awards_summary.php?id=256}{URL})
\item[2010]
Atlantic Halibut Assessment Science Peer Review Meeting, Fisheries and
Oceans, Dartmouth, NS, Canada.
\item[2007--09]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) Distributed Graduate Seminar, in association with the
Working Group \emph{Finding Common Ground in Marine Conservation and
Management} led by Ray Hilborn and Boris Worm.
(\href{http://www.nceas.ucsb.edu/projects/12307}{URL})
\end{description}

@@

Reviewer for Science, Canadian Journal of Fisheries and Aquatic
Sciences, Fish and Fisheries, Fisheries Research, ICES Journal of Marine
Science, Ecological Applications, Conservation Biology, Proceedings B,
Ecology, Marine Policy, Population Ecology, Journal of Applied Ecology,
International Journal of Tropical Biology and Conservation, Biological
Conservation, Diversity and Distributions, Oikos, Journal of
Environmental Management, Endangered Species Research, Aquatic
Conservation, NSERC Discovery Grants
